---
title: "Rec and Tourism Delta Public Version"
author: "Isaac T. Sanchez"
date: "`r Sys.Date()`"
output: html_document
---

## 1) Setup: 

This public-facing workflow is shown in three chunks. Additional plots and analyses are omitted because they are still under development or depend on restricted materials. However, no credentials are required for public reproduction of this part as this repository uses local extract files rather than live API calls.

The visitor-sector grouping was constructed to approximate methods described by Dean Runyan Associates (2024), *The Economic Impact of Travel in California*, prepared for Visit California.

Excel table shows outputs deemed adequate for summaries of the Visitor Sector for our study: DOI:...

Workflow made for significance testing FIGURE 5 in manuscript, supplemental materials not used marked at pane above chunk(s)

```{r setup}

library(dplyr)
library(emmeans)
library(forcats)
library(ggplot2)
library(patchwork)
library(purrr)
library(readxl)
library(sandwich)
library(stringr)
library(tidyr)

# Repo Inputs excel sheets in folder with this R-Project:
# - Water Raw: Hydrology_By_Year_Weighted
# - GDP by industry: GDP by Individual Industry
Water_raw <- read_excel("Data//Hydrology_By_Year_Weighted.xlsx", sheet = 1)
GDP_by_industry <- read_excel("Data//GDP by Individual Industry.xlsx", sheet =1)

# Hydrology Year condition levels
COND_LEVELS <- c("Critical", "Dry", "Below Normal", "Above Normal", "Wet")

# Color Palette
cond_pal <- c(
  "Critical" = "red4",
  "Dry" = "red1",
  "Below Normal" = "lightcoral",
  "Above Normal" = "deepskyblue1",
  "Wet" = "dodgerblue4"
)

# making sure data is masked to each county accordingly via FIPS:
geo_fips <- c(
  Sacramento = "06067",
  Solano = "06095",
  `Contra Costa` = "06013",
  Yolo = "06113",
  `San Joaquin` = "06077"
)
```

## 2) Wrangling Data

```{r wrangle}

# Convert year columns to long format and keep non-missing values
pick_col <- function(nms, patterns) {
  idx <- purrr::map(patterns, ~ which(stringr::str_detect(tolower(nms), .x))) |>
    unlist()
  if (length(idx) == 0) NA_character_ else nms[idx[1]]
}

clean_desc <- function(x) {
  stringr::str_squish(stringr::str_to_lower(x))
}

pull_line <- function(df, patterns) {
  df %>%
    dplyr::filter(stringr::str_detect(desc, paste0(patterns, collapse = "|"))) %>%
    dplyr::group_by(GeoFIPS, GeoName, Year) %>%
    dplyr::summarise(val_mil = sum(DataValue, na.rm = TRUE) / 1000, .groups = "drop")
}

# Join BEA and hydrology by year ------------------------------------------

water_clean <- Water_raw |>
  janitor::clean_names()

names(water_clean)

wy <- water_clean |>
  dplyr::transmute(
    Year = as.integer(.data[["year"]]),
    Unimp_Runoff_Type = .data[["year_type_wy"]] |>
      stringr::str_squish() |>
      stringr::str_to_title()
  ) |>
  dplyr::mutate(
    Unimp_Runoff_Type = factor(
      Unimp_Runoff_Type,
      levels = COND_LEVELS,
      ordered = TRUE
    )
  )

# GDP wide to long
nms <- names(GDP_by_industry)
geo_col <- pick_col(nms, c("^geo[_ -]?fips$", "^geofips$"))
name_col <- pick_col(nms, c("^geo[_ -]?name$", "^geoname$"))
desc_col <- pick_col(nms, c("^desc(ription)?$", "^line[_ -]?desc"))

year_cols <- nms[stringr::str_detect(nms, "^(?:x)?(?:19|20)\\d{2}$")]

gdp_long <- GDP_by_industry %>%
  dplyr::rename(
    GeoFIPS = dplyr::all_of(geo_col),
    GeoName_raw = dplyr::all_of(name_col),
    LineDescription = dplyr::all_of(desc_col)
  ) %>%
  tidyr::pivot_longer(
    dplyr::all_of(year_cols),
    names_to = "Year",
    values_to = "DataValue"
  ) %>%
  dplyr::mutate(
    Year = as.integer(stringr::str_replace(Year, "^x", "")),
    GeoFIPS = as.character(GeoFIPS),
    GeoName = stringr::str_remove(GeoName_raw, ",\\s*CA$"),
    DataValue = suppressWarnings(as.numeric(DataValue)),
    desc = clean_desc(LineDescription)
  ) %>%
  dplyr::filter(
    !is.na(Year),
    !is.na(DataValue),
    GeoFIPS %in% unname(geo_fips)
  ) %>%
  dplyr::select(GeoFIPS, GeoName, Year, LineDescription, desc, DataValue)

# Visitor-sector related naming patterns, carry-over methods from Dean Runyan Associates (2024)
nm_af_sector <- "^accommodation and food services$"
nm_aer_sector <- "^arts, entertainment, and recreation$"
nm_foodstore <- "^food and beverage stores$"
nm_gas <- "^gasoline stations$"
nm_retail <- "^retail trade$"
nm_clothing <- "^clothing and clothing accessories stores$"
nm_sportbook <- "^sporting goods, hobby, musical instrument, and book stores$"
nm_genmerch <- "^general merchandise stores$"
nm_miscstore <- "^miscellaneous store retailers$"
nm_air_sched <- "^scheduled passenger air transportation$"
nm_air_supp <- "^support activities for air transportation$"
nm_brewers <- "^breweries$|^wineries$|^distilleries$|^breweries, wineries, and distilleries$|^breweries, wineries, distilleries$"
nm_travel_ag <- "^travel agencies$"
nm_conventions <- "^convention and trade show organizers$"
nm_transit_gp <- "^transit and ground passenger transportation$"
nm_scenic <- "^scenic and sightseeing transportation$"
nm_rail <- "^rail transportation$"
nm_water <- "^water transportation$"
nm_urban <- "^urban transit systems$"
nm_interurban <- "^interurban and rural bus transportation$"
nm_taxi <- "^taxi and limousine service$"
nm_charter <- "^charter bus industry$"
nm_car_rent <- "^passenger car rental$"
nm_truck_rent <- "^truck, trailer, and rv rental and leasing$"
nm_parking <- "^parking lots and garages$"
nm_tour_ops <- "^tour operators$"

AF <- pull_line(gdp_long, nm_af_sector) %>%
  dplyr::rename(AccomFood = val_mil)

AER <- pull_line(gdp_long, nm_aer_sector) %>%
  dplyr::rename(ArtsEntRec = val_mil)

LocalTrans <- dplyr::bind_rows(
  pull_line(gdp_long, nm_transit_gp),
  pull_line(gdp_long, nm_scenic),
  pull_line(gdp_long, nm_rail),
  pull_line(gdp_long, nm_water),
  pull_line(gdp_long, nm_urban),
  pull_line(gdp_long, nm_interurban),
  pull_line(gdp_long, nm_taxi),
  pull_line(gdp_long, nm_charter),
  pull_line(gdp_long, nm_car_rent),
  pull_line(gdp_long, nm_truck_rent),
  pull_line(gdp_long, nm_parking),
  pull_line(gdp_long, nm_tour_ops)
) %>%
  dplyr::group_by(GeoFIPS, GeoName, Year) %>%
  dplyr::summarise(LocalTransport = sum(val_mil, na.rm = TRUE), .groups = "drop")

FoodStores <- pull_line(gdp_long, nm_foodstore) %>%
  dplyr::rename(FoodStores = val_mil)

Gasoline <- pull_line(gdp_long, nm_gas) %>%
  dplyr::rename(Gasoline = val_mil)

RetailKeep <- dplyr::bind_rows(
  pull_line(gdp_long, nm_clothing),
  pull_line(gdp_long, nm_sportbook),
  pull_line(gdp_long, nm_genmerch),
  pull_line(gdp_long, nm_miscstore)
) %>%
  dplyr::group_by(GeoFIPS, GeoName, Year) %>%
  dplyr::summarise(RetailKeep = sum(val_mil, na.rm = TRUE), .groups = "drop")

RetailTotal <- pull_line(gdp_long, nm_retail) %>%
  dplyr::rename(RetailTotal = val_mil)

RetailTourism <- RetailTotal %>%
  dplyr::full_join(FoodStores, by = c("GeoFIPS", "GeoName", "Year")) %>%
  dplyr::full_join(Gasoline, by = c("GeoFIPS", "GeoName", "Year")) %>%
  dplyr::full_join(RetailKeep, by = c("GeoFIPS", "GeoName", "Year")) %>%
  dplyr::mutate(
    RetailSales = dplyr::coalesce(
      RetailKeep,
      pmax(
        dplyr::coalesce(RetailTotal, 0) -
          dplyr::coalesce(FoodStores, 0) -
          dplyr::coalesce(Gasoline, 0),
        0
      )
    )
  ) %>%
  dplyr::select(GeoFIPS, GeoName, Year, RetailSales, FoodStores, Gasoline)

AirTrans <- dplyr::bind_rows(
  pull_line(gdp_long, nm_air_sched),
  pull_line(gdp_long, nm_air_supp)
) %>%
  dplyr::group_by(GeoFIPS, GeoName, Year) %>%
  dplyr::summarise(AirTransport = sum(val_mil, na.rm = TRUE), .groups = "drop")

BeverageProd <- pull_line(gdp_long, nm_brewers) %>%
  dplyr::rename(BeverageProd = val_mil)

TravelServices <- dplyr::bind_rows(
  pull_line(gdp_long, nm_travel_ag),
  pull_line(gdp_long, nm_conventions)
) %>%
  dplyr::group_by(GeoFIPS, GeoName, Year) %>%
  dplyr::summarise(TravelServices = sum(val_mil, na.rm = TRUE), .groups = "drop")

# Aggregate regional yearly totals
region_year <- AF %>%
  dplyr::full_join(AER, by = c("GeoFIPS", "GeoName", "Year")) %>%
  dplyr::full_join(LocalTrans, by = c("GeoFIPS", "GeoName", "Year")) %>%
  dplyr::full_join(RetailTourism, by = c("GeoFIPS", "GeoName", "Year")) %>%
  dplyr::full_join(AirTrans, by = c("GeoFIPS", "GeoName", "Year")) %>%
  dplyr::full_join(BeverageProd, by = c("GeoFIPS", "GeoName", "Year")) %>%
  dplyr::full_join(TravelServices, by = c("GeoFIPS", "GeoName", "Year")) %>%
  dplyr::group_by(Year) %>%
  dplyr::summarise(
    AccomFood = sum(AccomFood, na.rm = TRUE),
    ArtsEntRec = sum(ArtsEntRec, na.rm = TRUE),
    LocalTransport = sum(LocalTransport, na.rm = TRUE),
    RetailSales = sum(RetailSales, na.rm = TRUE),
    FoodStores = sum(FoodStores, na.rm = TRUE),
    Gasoline = sum(Gasoline, na.rm = TRUE),
    AirTransport = sum(AirTransport, na.rm = TRUE),
    BeverageProd = sum(BeverageProd, na.rm = TRUE),
    TravelServices = sum(TravelServices, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    Total = AccomFood + ArtsEntRec + LocalTransport + RetailSales +
      FoodStores + Gasoline + AirTransport + BeverageProd + TravelServices
  ) %>%
  dplyr::left_join(wy, by = "Year")

# Model inference:
# Percent difference from long-run mean -----------------------------------

overall_mean <- mean(region_year$Total, na.rm = TRUE)

type_summary <- region_year |>
  dplyr::group_by(Unimp_Runoff_Type) |>
  dplyr::summarise(
    pct_diff = 100 * (mean(Total, na.rm = TRUE) / overall_mean - 1),
    .groups = "drop"
  )


```


### 3) The two plots

```{r plots}

axis_text_size <- 14   
axis_title_size <- 14
axis_color <- "gray20" 

# Plot A: by-year aggregate totals
p1 <- ggplot2::ggplot(
  region_year,
  ggplot2::aes(x = factor(Year), y = Total, fill = Unimp_Runoff_Type)
) +
  ggplot2::geom_col(width = 0.8, colour = "gray15", linewidth = 0.15) +
  ggplot2::scale_fill_manual(values = cond_pal, drop = FALSE, name = "") +
  ggplot2::scale_y_continuous(
    labels = \(x) paste0(x / 1000, "M"),
    limits = c(0, 20000),
    expand = ggplot2::expansion(mult = c(0, 0.05))
  ) +
  ggplot2::labs(
    title = "Visitor-Related Earnings: Five-County Total by Year",
    x = NULL,
    y = "Millions of dollars"
  ) +
  ggplot2::theme_minimal(base_size = 11) +
  ggplot2::theme(
    plot.title = ggplot2::element_text(hjust = 0.5),

# AXES TEXT 
    axis.text.x = ggplot2::element_text(
      angle = 45,
      hjust = 1,
      size = axis_text_size,
      colour = axis_color
    ),
    axis.text.y = ggplot2::element_text(
      size = axis_text_size,
      colour = axis_color
    ),

# AXES TITLES (match subtitle size)
    axis.title.y = ggplot2::element_text(
      size = axis_title_size,
      colour = axis_color
    ),

# GRID cleanup
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.minor.x = ggplot2::element_blank(),
    panel.grid.minor.y = ggplot2::element_blank(),

# LEGEND (condition labels)
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.text = ggplot2::element_text(size = axis_text_size)
  ) +
  ggplot2::guides(fill = ggplot2::guide_legend(nrow = 1, byrow = TRUE))

# Plot B: percent difference from the long-run mean
p_type_pct_sig <- ggplot2::ggplot(
  type_summary,
  ggplot2::aes(x = Unimp_Runoff_Type, y = pct_diff, fill = Unimp_Runoff_Type)
) +
  ggplot2::geom_hline(
    yintercept = 0,
    linetype = "dashed",
    linewidth = 0.4,
    colour = "gray35"
  ) +
  ggplot2::geom_col(
    width = 0.75,
    colour = "gray10",
    linewidth = 0.3
  ) +
  ggplot2::scale_fill_manual(values = cond_pal, guide = "none") +
  ggplot2::scale_y_continuous(
    labels = \(x) paste0(round(x), "%"),
    limits = c(-30, 30),
    expand = ggplot2::expansion(mult = c(0.05, 0.08))
  ) +
  ggplot2::labs(
    title = NULL,
    x = NULL,
    y = NULL
  ) +
  ggplot2::theme_minimal(base_size = 13) +
  ggplot2::theme(
    panel.grid = ggplot2::element_blank(),

    panel.border = ggplot2::element_rect(
      colour = "gray20",
      fill = NA,
      linewidth = 0.6
    ),

    axis.ticks = ggplot2::element_blank(),

    # AXIS TEXT (final adjustments)
    axis.text.x = ggplot2::element_text(
      size = axis_text_size,
      colour = axis_color
    ),
    axis.text.y = ggplot2::element_text(
      size = axis_text_size,
      colour = axis_color
    )
  )
# Print plots
p1
p_type_pct_sig

```


```{r GDP significance}

COND_LEVELS <- c("Critical", "Dry", "Below Normal", "Above Normal", "Wet")

within_period_sig_gdp <- function(dat, period_label) {
  dat2 <- dat |>
    dplyr::filter(
      !is.na(Total),
      !is.na(Unimp_Runoff_Type),
      !is.na(Year)
    ) |>
    dplyr::mutate(
      Condition = factor(
        Unimp_Runoff_Type,
        levels = COND_LEVELS,
        ordered = TRUE
      ) |>
        forcats::fct_drop(),
      Year = as.numeric(Year)
    )

  condition_counts <- dat2 |>
    dplyr::count(Condition, name = "n_years")

  dat2 <- dat2 |>
    dplyr::semi_join(
      condition_counts |> dplyr::filter(n_years >= 2),
      by = "Condition"
    ) |>
    droplevels()

  if (nrow(dat2) < 4 || dplyr::n_distinct(dat2$Condition) < 2) {
    return(
      tibble::tibble(
        Period = period_label,
        Condition = factor(COND_LEVELS, levels = COND_LEVELS, ordered = TRUE),
        Estimate = NA_real_,
        CI_low = NA_real_,
        CI_high = NA_real_,
        pct = NA_real_,
        pcl = NA_real_,
        pcu = NA_real_,
        p_bh = NA_real_,
        sig_0_01 = FALSE,
        sig_0_05 = FALSE,
        note = "Skipped: too few observations per hydrology class"
      )
    )
  }

  mod <- stats::lm(Total ~ Condition + Year, data = dat2)

  hat_max <- max(stats::hatvalues(mod), na.rm = TRUE)

  if (hat_max >= 0.999) {
    return(
      tibble::tibble(
        Period = period_label,
        Condition = factor(COND_LEVELS, levels = COND_LEVELS, ordered = TRUE),
        Estimate = NA_real_,
        CI_low = NA_real_,
        CI_high = NA_real_,
        pct = NA_real_,
        pcl = NA_real_,
        pcu = NA_real_,
        p_bh = NA_real_,
        sig_0_01 = FALSE,
        sig_0_05 = FALSE,
        note = "Skipped: HC3 unstable because leverage is near 1"
      )
    )
  }

year_mean <- mean(dat2$Year, na.rm = TRUE)

# HC3 robust covariance matrix
vc <- sandwich::vcovHC(
  mod,
  type = "HC3"
)

# Estimated marginal means evaluated at the average year
em <- emmeans::emmeans(
  mod,
  ~ Condition,
  at = list(Year = year_mean),
  vcov. = vc
)

  eff <- emmeans::contrast(em, "eff", adjust = "BH")
  seff <- summary(eff, infer = TRUE)
  sem <- summary(em)

  lcl <- if ("lower.CL" %in% names(seff)) seff$lower.CL else seff$asymp.LCL
  ucl <- if ("upper.CL" %in% names(seff)) seff$upper.CL else seff$asymp.UCL

  gm <- mean(sem$emmean, na.rm = TRUE)

  tibble::tibble(
    Period = period_label,
    Condition = factor(
      as.data.frame(em)$Condition,
      levels = COND_LEVELS,
      ordered = TRUE
    ),
    Estimate = seff$estimate,
    CI_low = lcl,
    CI_high = ucl,
    pct = 100 * Estimate / gm,
    pcl = 100 * CI_low / gm,
    pcu = 100 * CI_high / gm,
    p_bh = seff$p.value,
    sig_0_01 = p_bh < 0.01,
    sig_0_05 = p_bh < 0.05,
    note = NA_character_
  )
}

gdp_sig_results <- dplyr::bind_rows(
  within_period_sig_gdp(
    region_year |> dplyr::filter(Year <= 2009),
    "Pre-2010"
  ),
  within_period_sig_gdp(
    region_year |> dplyr::filter(Year >= 2010),
    "Post-2010"
  ),
  within_period_sig_gdp(
    region_year,
    "Full period"
  )
) |>
  dplyr::arrange(Period, Condition)

gdp_sig_table <- gdp_sig_results |>
  dplyr::mutate(
    Estimate_fmt = dplyr::if_else(
      is.na(pct),
      NA_character_,
      paste0(
        sprintf("%.1f", pct),
        "%",
        dplyr::case_when(
          sig_0_01 ~ " *",
          TRUE ~ ""
        )
      )
    ),
    Range = dplyr::if_else(
      is.na(pcl) | is.na(pcu),
      NA_character_,
      paste0(
        sprintf("%.1f", pcl),
        "%, ",
        sprintf("%.1f", pcu),
        "%"
      )
    )
  ) |>
  dplyr::select(
    Period,
    Condition,
    Estimate = Estimate_fmt,
    Range,
    p_bh,
    note
  )

gdp_sig_table
```

```{r sector-share-table}

# Visitor sector composition (% of total) by year
# Built directly from BEA aggregation (see wrangle chunk above)

sector_share <- region_year %>%
  dplyr::select(
    Year,
    AccomFood,
    ArtsEntRec,
    LocalTransport,
    RetailSales,
    FoodStores,
    Gasoline,
    AirTransport,
    BeverageProd,
    TravelServices,
    Total
  ) %>%
  dplyr::mutate(
    dplyr::across(
      -c(Year, Total),
      ~ 100 * (.x / Total)
    )
  ) %>%
  dplyr::select(-Total) %>%
  dplyr::arrange(Year)

# Clean names 
sector_share_clean <- sector_share %>%
  dplyr::rename(
    `Accommodation & Food` = AccomFood,
    `Arts, Entertainment, Recreation` = ArtsEntRec,
    `Local Transport` = LocalTransport,
    `Retail (Tourism-related)` = RetailSales,
    `Food Stores` = FoodStores,
    `Gasoline` = Gasoline,
    `Air Transport` = AirTransport,
    `Beverage Production` = BeverageProd,
    `Travel Services` = TravelServices
  )

# round up for legibility
sector_share_clean <- sector_share_clean %>%
  dplyr::mutate(
    dplyr::across(-Year, ~ round(.x, 1))
  )

# PERCENT SHARE USED FOR FIGURE 5 AND DISCUSSION SECTION 
sector_share_clean
```

```{r audit}
# =========================
# BEA GDP MODEL AUDIT
# =========================

COND_LEVELS <- c(
  "Critical",
  "Dry",
  "Below Normal",
  "Above Normal",
  "Wet"
)

audit_bea_model <- function(dat, label) {

  dat2 <- dat %>%
    dplyr::filter(
      !is.na(Total),
      !is.na(Unimp_Runoff_Type),
      !is.na(Year)
    ) %>%
    dplyr::mutate(
      Condition = factor(
        Unimp_Runoff_Type,
        levels = COND_LEVELS
      ) |>
        forcats::fct_drop()
    )

  mod <- stats::lm(
    Total ~ Condition + Year,
    data = dat2
  )

  tibble::tibble(
    Model = label,
    n = stats::nobs(mod),
    n_conditions = nlevels(dat2$Condition),
    R2 = summary(mod)$r.squared,
    Adj_R2 = summary(mod)$adj.r.squared,
    RMSE = sqrt(mean(residuals(mod)^2)),
    Max_Leverage = max(hatvalues(mod)),
    Max_CooksD = max(cooks.distance(mod)),
    Influential_Points = sum(
      cooks.distance(mod) > 4 / stats::nobs(mod)
    )
  )
}

bea_audit <- dplyr::bind_rows(

  audit_bea_model(
    region_year,
    "Full Period"
  ),

  audit_bea_model(
    region_year %>%
      dplyr::filter(Year <= 2009),
    "Pre-2010"
  ),

  audit_bea_model(
    region_year %>%
      dplyr::filter(Year >= 2010),
    "Post-2010"
  )

)

bea_audit
```