---
title: "Stripped Bass Fisheries"
author: "See CC Licensing Information"
date: "`r Sys.Date()`"
output: html_document
---
## 1) Setup:

Excel sheets used for this framework may be found in same folder, make path and should work as simply

Workflow made for significance testing FIGURE 4 in manuscript, supplemental materials not used marked at pane above chunk(s)

```{r setup, include=FALSE}

library(broom)
library(dplyr)
library(devEMF)
library(emmeans)
library(forcats)
library(ggplot2)
library(ggdist)
library(Hmisc)
library(kableExtra)
library(lme4)
library(lubridate)
library(officer)
library(patchwork)
library(purrr)
library(readxl)
library(rlang)
library(rsvg)
library(readr)
library(sandwich)
library(svglite)
library(stringr)
library(tidyr)
library(zoo)
library(showtext)

Adult_Bass <- readxl::read_excel("Data//Adult Striped Bass DFW.xlsx", sheet = 1)
Zero_Age_Bass <- readxl::read_excel("Data//Index 0-age Striped Bass.xlsx", sheet = 1)

```


```{r striped bass data clean up}

# hydrology class order
COND_LEVELS <- c("Critical", "Dry", "Below Normal", "Above Normal", "Wet")


# Adult striped bass clean
# Main columns pulled:
# - release_date
# - common_name
# - Weighted Year Type 82/18

adult_bass_clean <- Adult_Bass %>%
  dplyr::select(
    release_id = release_ID,
    release_date = release_date,
    release_location = release_location,
    release_method = release_method,
    common_name = common_name,
    release_fl_cm = release_FL_cm,
    sex = sex,
    age = age,
    count = count,
    water_year_date = `water year date`,
    condition_raw = `Weighted Year Type`
  ) %>%
  dplyr::mutate(
    release_date = as.Date(release_date),
    year = lubridate::year(release_date),
    common_name = stringr::str_squish(as.character(common_name)),
    condition_raw = stringr::str_squish(as.character(condition_raw)),
    Condition = dplyr::case_when(
      stringr::str_detect(condition_raw, stringr::regex("Critical|Extreme Drought", ignore_case = TRUE)) ~ "Critical",
      stringr::str_detect(condition_raw, stringr::regex("^Dry|\\bDry Year\\b", ignore_case = TRUE)) ~ "Dry",
      stringr::str_detect(condition_raw, stringr::regex("Below Normal", ignore_case = TRUE)) ~ "Below Normal",
      stringr::str_detect(condition_raw, stringr::regex("Above Normal", ignore_case = TRUE)) ~ "Above Normal",
      stringr::str_detect(condition_raw, stringr::regex("^Wet|\\bWet Year\\b|Moderate Wet", ignore_case = TRUE)) ~ "Wet",
      TRUE ~ NA_character_
    ),
    Condition = factor(Condition, levels = COND_LEVELS, ordered = TRUE)
  ) %>%
  dplyr::filter(common_name == "Striped Bass")


# Age-0 striped bass clean
# Main columns pulled:
# - YEAR
# - INDEX DATE
# - TOTAL INDEX
# - Unimpaired Weighted Drainage 82/18

age0_bass_clean <- Zero_Age_Bass%>%
  dplyr::select(
    year = YEAR,
    index_date = `INDEX DATE`,
    delta_index = `DELTA INDEX`,
    suisun_bay_index = `SUISUN BAY INDEX`,
    total_index = `TOTAL INDEX`,
    water_year_date = `Water Year Date`,
    condition_raw = `Weighted Year Type`
  ) %>%
  dplyr::mutate(
    index_date = suppressWarnings(lubridate::mdy(index_date)),
    year = as.integer(year),
    total_index = as.numeric(total_index),
    condition_raw = stringr::str_squish(as.character(condition_raw)),
    Condition = dplyr::case_when(
      stringr::str_detect(condition_raw, stringr::regex("Critical|Extreme Drought", ignore_case = TRUE)) ~ "Critical",
      stringr::str_detect(condition_raw, stringr::regex("^Dry|\\bDry Year\\b", ignore_case = TRUE)) ~ "Dry",
      stringr::str_detect(condition_raw, stringr::regex("Below Normal", ignore_case = TRUE)) ~ "Below Normal",
      stringr::str_detect(condition_raw, stringr::regex("Above Normal", ignore_case = TRUE)) ~ "Above Normal",
      stringr::str_detect(condition_raw, stringr::regex("^Wet|\\bWet Year\\b|Moderate Wet", ignore_case = TRUE)) ~ "Wet",
      TRUE ~ NA_character_
    ),
    Condition = factor(Condition, levels = COND_LEVELS, ordered = TRUE)
  )


# Quick Checks
# Check that hydrology classes were standardized correctly
check_levels <- function(data, name) {
  cat("\n", name, "\n", sep = "")
  print(levels(data$Condition))
  print(table(data$Condition, useNA = "ifany"))
  invisible(data)
}

check_levels(adult_bass_clean, "adult_bass_clean")
check_levels(age0_bass_clean, "age0_bass_clean")



# Quick checks
dplyr::glimpse(adult_bass_clean)
dplyr::glimpse(age0_bass_clean)

#adult_bass_clean %>%
#  summarise(
#    n_missing_year = sum(is.na(year)),
#    n_missing_condition = sum(is.na(Condition)),
#    n_missing_count = sum(is.na(count))
#  )

# glimpse(Adult_Bass)

```


```{r striped bass parameters and data clean}

# one annual table per striped bass dataset
# This mirrors the recreation workflow, but removes season and location.
# We focus on annual response values by hydrology class.
COND_LEVELS <- c("Critical", "Dry", "Below Normal", "Above Normal", "Wet")


# Adult striped bass annual table
# Columns used from cleaned table:
# - year
# - release_date
# - Condition

adult_bass_annual <- adult_bass_clean %>%
  dplyr::filter(!is.na(year), !is.na(Condition)) %>%
  dplyr::group_by(year, Condition) %>%
  dplyr::summarise(
    Value = sum(count, na.rm = TRUE),
    Date = as.Date(paste0(year, "-01-01")),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    Activity = "Adult Striped Bass",
    Condition = factor(Condition, levels = COND_LEVELS, ordered = FALSE)
  )


# Age-0 striped bass annual table
# Columns used from cleaned table:
# - year
# - index_date
# - total_index
# - Condition

age0_bass_annual <- age0_bass_clean %>%
  dplyr::filter(!is.na(year), !is.na(total_index), !is.na(Condition)) %>%
  dplyr::transmute(
    Activity = "Age-0 Striped Bass",
    Year = year,
    Date = dplyr::coalesce(index_date, as.Date(paste0(year, "-01-01"))),
    Value = as.numeric(total_index),
    Condition = factor(Condition, levels = COND_LEVELS, ordered = FALSE)
  )

# Fix column names to match
adult_bass_annual <- adult_bass_annual %>%
  dplyr::rename(Year = year)

adult_bass_annual <- adult_bass_clean %>%
  dplyr::filter(!is.na(year), !is.na(Condition)) %>%
  dplyr::group_by(year, Condition) %>%
  dplyr::summarise(
    Value = sum(count, na.rm = TRUE),
    Date = as.Date(sprintf("%d-01-01", dplyr::first(year))),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    Activity = "Adult Striped Bass",
    Condition = factor(Condition, levels = COND_LEVELS, ordered = FALSE)
  ) %>%
  dplyr::rename(Year = year)

# Bind into one striped bass analysis table

striped_bass_all_raw <- dplyr::bind_rows(
  adult_bass_annual,
  age0_bass_annual
)

striped_bass_all <- striped_bass_all_raw %>%
  dplyr::filter(
    !is.na(Activity),
    !is.na(Year),
    !is.na(Date),
    !is.na(Value),
    !is.na(Condition)
  ) %>%
  dplyr::mutate(
    Activity = factor(
      Activity,
      levels = c("Adult Striped Bass", "Age-0 Striped Bass")
    ),
    Condition = factor(Condition, levels = COND_LEVELS, ordered = TRUE)
  )


# Quick checks
tibble::tibble(
  n_adult_annual = nrow(adult_bass_annual),
  n_age0_annual = nrow(age0_bass_annual),
  n_total = nrow(striped_bass_all)
)

striped_bass_all %>%
  dplyr::count(Activity, Condition) %>%
  tidyr::complete(Activity, Condition, fill = list(n = 0))

```

```{r striped bass helper functions, include=FALSE}

# Shared striped bass model helpers
BASELINE <- "Below Normal"
EMM_WEIGHTS_GLOBAL <- "equal"
ROBUST_SE <- TRUE
HC_TYPE <- "HC3"

vcovHC_psd <- function(mod, type = "HC3") {
  vc <- sandwich::vcovHC(mod, type = type)
  vc <- as.matrix(vc)
  vc <- (vc + t(vc)) / 2

  ev <- tryCatch(
    eigen(vc, symmetric = TRUE, only.values = TRUE)$values,
    error = function(e) NA_real_
  )

  if (any(!is.finite(ev)) || any(ev < -1e-8)) {
    if (requireNamespace("Matrix", quietly = TRUE)) {
      vc <- as.matrix(Matrix::nearPD(vc, corr = FALSE)$mat)
    }
  }

  vc
}

safe_emm <- function(model, specs, weights = EMM_WEIGHTS_GLOBAL, at = list()) {
  if (ROBUST_SE) {
    vc <- vcovHC_psd(model, type = HC_TYPE)
    emmeans::emmeans(model, specs, weights = weights, at = at, vcov. = vc)
  } else {
    emmeans::emmeans(model, specs, weights = weights, at = at)
  }
}

```

##  WITHIN-PERIOD SETUP FOR STRIPED BASS, USED TO MARK SIGNIFICANCE IN FIGURE 4 STRIPED BASS

```{r striped bass period plots with significance}


# Striped bass by period:
# % difference from across-class average
COND_LEVELS <- c("Critical", "Dry", "Below Normal", "Above Normal", "Wet")


# Figure knobs
STAR_COLOR <- "red4"
STAR_PAD <- 18
STAR_SIZE <- 8

Y_MIN <- -120
Y_MAX <- 220

ERRBAR_LWD <- 0.6
ERRBAR_CAP <- 0.28

POINT_SIZE <- 10
POINT_SHAPE <- 22
POINT_STROKE <- 0.7

TITLE_SIZE <- 18
STRIP_SIZE <- 15
AXIS_SIZE <- 13
AXIS_TITLE_SIZE <- 13
LEGEND_SIZE <- 12
LEGEND_TITLE_SIZE <- 13

cond_pal <- c(
  "Critical" = "red4",
  "Dry" = "red1",
  "Below Normal" = "lightcoral",
  "Above Normal" = "deepskyblue1",
  "Wet" = "dodgerblue4"
)


# Build period-coded data
bass_period_df <- striped_bass_all %>%
  dplyr::mutate(
    Period = dplyr::case_when(
      Year >= 1969 & Year <= 1999 ~ "1969-1999",
      Year >= 2000 & Year <= 2022 ~ "2000-2022",
      TRUE ~ NA_character_
    ),
    Period = factor(Period, levels = c("1969-1999", "2000-2022")),
    Condition = factor(Condition, levels = COND_LEVELS, ordered = TRUE)
  ) %>%
  dplyr::filter(!is.na(Period), !is.na(Value), !is.na(Condition))


# Helper function
# % difference from across-class average within each Activity x Period
emm_pct_vs_avg_period <- function(dat) {
  dat2 <- dat %>%
    dplyr::filter(!is.na(Value), !is.na(Condition), !is.na(Year)) %>%
    dplyr::mutate(
      Condition = factor(Condition, levels = COND_LEVELS) |> forcats::fct_drop(),
      Year = as.numeric(Year)
    ) %>%
    droplevels()

  if (nrow(dat2) < 2L || length(levels(dat2$Condition)) < 2L) {
    return(
      tibble::tibble(
        Condition = factor(COND_LEVELS, levels = COND_LEVELS, ordered = TRUE),
        diff = NA_real_,
        lcl = NA_real_,
        ucl = NA_real_,
        p_bh = NA_real_,
        pct = NA_real_,
        pcl = NA_real_,
        pcu = NA_real_
      )
    )
  }

  mod <- stats::lm(Value ~ Condition + Year, data = dat2)

  year_mean <- mean(dat2$Year, na.rm = TRUE)

  em <- safe_emm(
    mod,
    ~ Condition,
    at = list(Year = year_mean)
  )

  eff <- emmeans::contrast(em, "eff", adjust = "BH")
  seff <- summary(eff, infer = TRUE)
  sem <- summary(em)

  lcl <- if ("lower.CL" %in% names(seff)) seff$lower.CL else seff$asymp.LCL
  ucl <- if ("upper.CL" %in% names(seff)) seff$upper.CL else seff$asymp.UCL

  gm <- mean(sem$emmean, na.rm = TRUE)
  if (!is.finite(gm) || gm == 0) {
    gm <- NA_real_
  }

  tibble::tibble(
    Condition = factor(as.data.frame(em)$Condition, levels = COND_LEVELS, ordered = TRUE),
    diff = seff$estimate,
    lcl = lcl,
    ucl = ucl,
    p_bh = seff$p.value,
    pct = 100 * diff / gm,
    pcl = 100 * lcl / gm,
    pcu = 100 * ucl / gm
  ) %>%
    dplyr::arrange(Condition)
}
```

## WITHIN PERIOD SIGNIFICANCE TABLE FOR STRIPED BASS FIGURE 4: 

```{r within-period significance for excel panels}
# Within-period significance STRIPED BASS
COND_LEVELS <- c("Critical", "Dry", "Below Normal", "Above Normal", "Wet")


# Helper function
within_period_sig <- function(dat) {
  
  dat2 <- dat %>%
    dplyr::filter(!is.na(Value), !is.na(Condition), !is.na(Year)) %>%
    dplyr::mutate(
      Condition = factor(Condition, levels = COND_LEVELS) |> forcats::fct_drop(),
      Year = as.numeric(Year)
    )
  
  if (nrow(dat2) < 2 || length(unique(dat2$Condition)) < 2) {
    return(NULL)
  }
  
# Model
  mod <- lm(Value ~ Condition + Year, data = dat2)
  
  year_mean <- mean(dat2$Year, na.rm = TRUE)
  
# EMMs
  em <- safe_emm(
    mod,
    ~ Condition,
    at = list(Year = year_mean)
  )
  
# "eff" = vs within-period mean
  eff <- emmeans::contrast(em, "eff", adjust = "BH")
  seff <- summary(eff, infer = TRUE)
  sem  <- summary(em)
  
# CI columns
  lcl <- if ("lower.CL" %in% names(seff)) seff$lower.CL else seff$asymp.LCL
  ucl <- if ("upper.CL" %in% names(seff)) seff$upper.CL else seff$asymp.UCL
  
# grand mean
  gm <- mean(sem$emmean, na.rm = TRUE)
  
  tibble::tibble(
    Condition = factor(as.data.frame(em)$Condition, levels = COND_LEVELS, ordered = TRUE),
    Estimate = seff$estimate,
    CI_low = lcl,
    CI_high = ucl,
    pct = 100 * Estimate / gm,
    pcl = 100 * CI_low / gm,
    pcu = 100 * CI_high / gm,
    p_bh = seff$p.value,
    sig_0_01 = p_bh < 0.01
  )
}


# Apply to each panel
results_within_period <- dplyr::bind_rows(

  striped_bass_all %>%
    dplyr::filter(Activity == "Age-0 Striped Bass", Year <= 1999) %>%
    within_period_sig() %>%
    dplyr::mutate(Activity = "Age-0", Period = "1969-1999"),

  striped_bass_all %>%
    dplyr::filter(Activity == "Age-0 Striped Bass", Year >= 2000) %>%
    within_period_sig() %>%
    dplyr::mutate(Activity = "Age-0", Period = "2000-2022"),

  striped_bass_all %>%
    dplyr::filter(Activity == "Adult Striped Bass", Year <= 1999) %>%
    within_period_sig() %>%
    dplyr::mutate(Activity = "Adult", Period = "1969-1999"),

  striped_bass_all %>%
    dplyr::filter(Activity == "Adult Striped Bass", Year >= 2000) %>%
    within_period_sig() %>%
    dplyr::mutate(Activity = "Adult", Period = "2000-2022")

) %>%
  dplyr::arrange(Activity, Period, Condition)


# Clean table 
results_within_period_table <- results_within_period %>%
  dplyr::mutate(
    Estimate_fmt = paste0(
      sprintf("%.1f", pct), "%",
      dplyr::case_when(
        sig_0_01 ~ " *",
        TRUE ~ ""
      )
    ),

    Range = paste0(
      sprintf("%.1f", pcl), "%, ",
      sprintf("%.1f", pcu), "%"
    ),

    p_bh = dplyr::case_when(
      is.na(p_bh) ~ "—",
      p_bh < 0.0001 ~ "<0.0001",
      TRUE ~ sprintf("%.4f", p_bh)
    )
  ) %>%
  dplyr::select(
    Activity,
    Period,
    Condition,
    Estimate = Estimate_fmt,
    Range,
    p_bh
  )

exists("safe_emm")
exists("vcovHC_psd")
exists("striped_bass_all")

# SUPPLEMENTARY TABLE 1: ESTIMATES FOR STRIPED BASS
results_within_period_table
```
## -------------Supplementary FIGURE NOT in PAPER------------------

```{r test between extremes Dry and Wet}

# Extreme swing analysis (Wet vs Critical)
extreme_swing <- function(dat) {
  
  dat2 <- dat %>%
    dplyr::filter(!is.na(Value), !is.na(Condition), !is.na(Year)) %>%
    dplyr::mutate(
      Condition = factor(Condition,
        levels = c("Critical","Dry","Below Normal","Above Normal","Wet")
      )
    )
  
  mod <- lm(Value ~ Condition + Year, data = dat2)
  year_mean <- mean(dat2$Year, na.rm = TRUE)
  
  em <- emmeans::emmeans(mod, ~ Condition, at = list(Year = year_mean))
  
# Contrast: Wet - Critical
  swing <- emmeans::contrast(
    em,
    list("Wet - Critical" = c(-1, 0, 0, 0, 1)),
    adjust = "none"
  )
  
  s <- summary(swing, infer = TRUE)
  sem <- summary(em)
  
  lcl <- if ("lower.CL" %in% names(s)) s$lower.CL else s$asymp.LCL
  ucl <- if ("upper.CL" %in% names(s)) s$upper.CL else s$asymp.UCL
  
  gm <- mean(sem$emmean, na.rm = TRUE)
  
  tibble::tibble(
    Estimate = s$estimate,
    CI_low = lcl,
    CI_high = ucl,
    pct = 100 * Estimate / gm,
    pcl = 100 * CI_low / gm,
    pcu = 100 * CI_high / gm,
    p_value = s$p.value
  )
}


#  activity + period
swing_results <- dplyr::bind_rows(

  striped_bass_all %>%
    dplyr::filter(Activity == "Age-0 Striped Bass", Year <= 1999) %>%
    extreme_swing() %>%
    dplyr::mutate(Activity = "Age-0", Period = "1969-1999"),

  striped_bass_all %>%
    dplyr::filter(Activity == "Age-0 Striped Bass", Year >= 2000) %>%
    extreme_swing() %>%
    dplyr::mutate(Activity = "Age-0", Period = "2000-2022"),

  striped_bass_all %>%
    dplyr::filter(Activity == "Adult Striped Bass", Year <= 1999) %>%
    extreme_swing() %>%
    dplyr::mutate(Activity = "Adult", Period = "1969-1999"),

  striped_bass_all %>%
    dplyr::filter(Activity == "Adult Striped Bass", Year >= 2000) %>%
    extreme_swing() %>%
    dplyr::mutate(Activity = "Adult", Period = "2000-2022")

)

## Kept here as supplementary
# Companion figure:
# Wet - Critical swing by period
# This figure shows hydrologic responsiveness as the contrast
# between Wet and Critical conditions within each period.
# Positive values mean Wet years are higher than Critical years.

swing_plot_df <- swing_results %>%
  dplyr::mutate(
    Activity = factor(
      Activity,
      levels = c("Age-0", "Adult")
    ),
    Period = factor(
      Period,
      levels = c("1969-1999", "2000-2022")
    ),
    panel = dplyr::case_when(
      Activity == "Age-0" ~ "a) Age-0 striped bass",
      Activity == "Adult" ~ "b) Adult striped bass",
      TRUE ~ NA_character_
    ),
    panel = factor(
      panel,
      levels = c("a) Age-0 striped bass", "b) Adult striped bass")
    ),
    star = dplyr::if_else(!is.na(p_value) & p_value < 0.01, "*", ""),
    y_star_raw = dplyr::if_else(
      !is.na(pct) & pct >= 0,
      pcu + 10,
      pcl - 10
    ),
    y_star = y_star_raw
  )

period_pal <- c(
  "1969-1999" = "gray55",
  "2000-2022" = "gray80"
)

p_swing <- ggplot2::ggplot(
  swing_plot_df,
  ggplot2::aes(x = Period, y = pct)
) +
  ggplot2::geom_hline(
    yintercept = 0,
    linewidth = 0.4,
    colour = "grey50"
  ) +
  ggplot2::geom_errorbar(
    ggplot2::aes(ymin = pcl, ymax = pcu),
    width = 0.14,
    linewidth = 0.6,
    colour = "black"
  ) +
  ggplot2::geom_col(
    ggplot2::aes(fill = Period),
    width = 0.62,
    colour = "black",
    linewidth = 0.35
  ) +
  ggplot2::geom_text(
    data = dplyr::filter(swing_plot_df, star != ""),
    ggplot2::aes(y = y_star, label = star),
    colour = "black",
    size = 8,
    fontface = "bold"
  ) +
  ggplot2::scale_fill_manual(
    values = period_pal,
    drop = FALSE,
    name = "Period"
  ) +
  ggplot2::facet_wrap(~ panel, ncol = 2) +
  ggplot2::labs(
    title = "Wet–Critical difference (\"hydrologic swing\") by period\n(Wet minus Critical conditions)",
    x = NULL,
    y = "% difference vs within-period average"
  ) +
  ggplot2::theme_minimal(base_size = 12) +
  ggplot2::theme(
    panel.grid.minor = ggplot2::element_blank(),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_line(
      linewidth = 0.35,
      colour = "grey85"
    ),
    strip.text = ggplot2::element_text(
      face = "bold",
      size = 14,
      colour = "gray15"
    ),
    axis.text.x = ggplot2::element_text(
      size = 13,
      colour = "gray20"
    ),
    axis.text.y = ggplot2::element_text(
      size = 13,
      colour = "gray20"
    ),
    axis.title.y = ggplot2::element_text(
      size = 13,
      colour = "gray20"
    ),
    legend.position = "bottom",
    legend.title = ggplot2::element_text(size = 12),
    legend.text = ggplot2::element_text(size = 11),
    panel.spacing = grid::unit(14, "pt"),
    plot.margin = grid::unit(c(16, 16, 16, 16), "pt"),
    plot.title = ggplot2::element_text(
      hjust = 0.5,
      face = "bold",
      size = 16
    )
  )

p_swing
swing_results


```

```{r audit}
# =========================
# STRIPED BASS MODEL AUDIT
# =========================

audit_bass_model <- function(dat, label) {

  dat2 <- dat %>%
    dplyr::filter(
      !is.na(Value),
      !is.na(Condition),
      !is.na(Year)
    ) %>%
    dplyr::mutate(
      Condition = factor(
        Condition,
        levels = COND_LEVELS
      ) |> forcats::fct_drop()
    )

  mod <- lm(
    Value ~ Condition + Year,
    data = dat2
  )

  cook <- cooks.distance(mod)

  tibble::tibble(
    Model = label,
    n = stats::nobs(mod),
    n_conditions = nlevels(dat2$Condition),
    R2 = summary(mod)$r.squared,
    Adj_R2 = summary(mod)$adj.r.squared,
    RMSE = sqrt(mean(residuals(mod)^2)),
    Max_Leverage = max(hatvalues(mod), na.rm = TRUE),
    Max_CooksD =
      if (all(is.na(cook))) NA_real_
      else max(cook, na.rm = TRUE),
    Influential_Points =
      if (all(is.na(cook))) NA_integer_
      else sum(
        cook > 4 / stats::nobs(mod),
        na.rm = TRUE
      )
  )
}

bass_audit <- dplyr::bind_rows(

  audit_bass_model(
    striped_bass_all %>%
      dplyr::filter(
        Activity == "Age-0 Striped Bass",
        Year <= 1999
      ),
    "Age-0 (1969-1999)"
  ),

  audit_bass_model(
    striped_bass_all %>%
      dplyr::filter(
        Activity == "Age-0 Striped Bass",
        Year >= 2000
      ),
    "Age-0 (2000-2022)"
  ),

  audit_bass_model(
    striped_bass_all %>%
      dplyr::filter(
        Activity == "Adult Striped Bass",
        Year <= 1999
      ),
    "Adult (1969-1999)"
  ),

  audit_bass_model(
    striped_bass_all %>%
      dplyr::filter(
        Activity == "Adult Striped Bass",
        Year >= 2000
      ),
    "Adult (2000-2022)"
  )

)

bass_audit
```